The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updated introduction to FThresholds paper

\begin{abstract}
	This note describes the \emph{Macaulay2} package \emph{FThresholds}.  This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
\end{abstract}

@@

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
This value is typically very difficult to calculate in general, and computing and estimating its value is the core of this \emph{Macaulay2} package.

Moreover, the more general family of \emph{$F$-thresholds} was also introduced. 
This family of numerical invariants have been the focus of intense study over the past fifteen years, with

There are three main sections in this paper, describing the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}. 
\begin{itemize}
\item{} \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
\item{} \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
\item{} \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
\end{itemize}

This package builds heavily upon the \emph{TestIdeals} package, which provides a broad range of functionality in prime characteristic commutative algebra.

>>>>

\begin{abstract}
	This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.  This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
\end{abstract}

@@

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
These numerical invariants are typically very difficult to calculate in general, and have been the 
focus of intense study over the past fifteen years.
This \emph{Macaulay2} package is centered around calculating 
and estimating the $F$-pure threshold and other $F$-thresholds.

There are three main sections in this paper, describing the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}. 
\begin{itemize}
\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
\item \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
\item \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
\end{itemize}

This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.
